APPM report - Draft

### 2022-12-09 paper_version/main.tex
minor change
draft conclusion and polish reference

\section*{Abstract}
A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero. It may range over many orders of magnitude: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral. A singularly perturbed problem arises from the $\lambda_D\to 0$ limit, which leads to peculiar issues in numerical algorithms when both regimes coexist, for instance, in the fringes of electric arcs and near electrodes. It is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$. More precisely, they should be \emph{asymptotic-preserving} (AP), in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.

An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.

@@

\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform_discrete}
In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. In the semi-discrete level, the equations to be solved in $\Omega_N$ are

@@

@@

\subsection{Case I: Quasi-1D Problem}
Noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e. $z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives. The (isentropic and collisionless) Euler-Maxwell system at the axis of symmetry reduces to
\begin{align*}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_*(n_*) = \varepsilon_*^{-2}q_*n_*E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align*}
which shares the same equations as the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Section \ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section \ref{sec:3d_ap_scheme}) restricted to the $z$-axis. The following initial conditions are used for both models
\begin{equation*}
    n_e(z,0) = n_i(z,0) = 1, u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z),\ \ \forall z \in [-0.1,0.1].
\end{equation*}
where $\chi$ is the characteristic function. The other variables are initially zero. The case for $\lambda = 1$ is tested. Fig. \ref{fig:z_axis_reduction} demonstrates good matching.

@@

Next, we perform a grid study. The norms of the solutions under mesh refinement are shown in Fig. \ref{fig:grid_study_3d}. Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not trivially accessible. Therefore, we demonstrate results generated by relatively coarse meshes. Tab. \ref{tab:grid_study_norm} lists $L^2$-norms of the solutions on different meshes, which indicates  robustness with respect to mesh refinement. To reveal more features of the solutions, in Fig. \ref{fig:grid_study_3d_clip_lambda-1e-1} and \ref{fig:grid_study_3d_clip_lambda-0} we plot the solutions at the cross-section generated by meshes of different sizes for $\lambda = 0.1$ and $0$. Qualitatively the same solutions are produced on meshes of different sizes.

@@

The stabilization proposed in Section \ref{sec:reform_discrete} is essential to achieve a stable result when $\lambda$ tends to zero. As is shown in Fig. \ref{fig:stabilization_comparison}, the scheme without stabilization tends to blow up when $\lambda$ is close to zero while the one with stabilization remains stable. 
\begin{figure}
    \centering
    \includegraphics{stabilizationComparision_stepVoltage.eps}
    \caption{Case II: Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
    \label{fig:stabilization_comparison}
\end{figure}

@@

\section{Conclusion}

\bibliography{ref}
\end{document}

>>>>

\section*{Abstract}
\todo{polish the abstract}

A key coefficient characterizing plasmas is the so-called Debye length $\lambda_D$, whose magnitude indicates to what extent net electric charges deviate from zero. It may range over many orders of magnitude: If $\lambda_D = \mathcal{O}(1)$ we face the non-neutral regime, while for $\lambda_D\to 0$ the plasma becomes quasi-neutral. A singularly perturbed problem arises from the $\lambda_D\to 0$ limit, which leads to peculiar issues in numerical algorithms when both regimes coexist, for instance, in the fringes of electric arcs and near electrodes. It is desired to design numerical schemes that are \emph{robust} for arbitrary $\lambda_D$. More precisely, they should be \emph{asymptotic-preserving} (AP), in the sense that the limit $\lambda_D\to 0$ of the scheme yields a viable discretization for the continuous limit model.

An asymptotic-preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We extend their scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. The scheme is designed to be AP as $\lambda_D \rightarrow 0$ and this is validated through numerical experiments. Besides, if the electromagnetic fields have to be modelled in an non-conducting region beyond the plasma domain, additional stabilization to accommodate Gauss's law is necessary.

@@

\subsubsection{Stabilization in $\Omega_N$} \label{sec:reform-discrete}
In Section \ref{sec:reform_continuous}, we have proposed a stabilization of the Maxwell system in the non-conducting domain $\Omega_N$ by introducing a Lagrange multiplier. In the semi-discrete level, the equations to be solved in $\Omega_N$ are

@@

The source code is published in \cite{yu2022}.

@@

\subsection{Case I: Quasi-1D Problem}
Noticing the radial symmetry of the domain as well as boundary conditions, we can simplify the governing equations defined at the axis of symmetry, i.e. $z$-axis in this case, thanks to vanishing radial components of the vector fields and their radial derivatives. The (isentropic and collisionless) Euler-Maxwell system at the axis of symmetry reduces to
\begin{align*}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z p_*(n_*) = \varepsilon_*^{-2}q_*n_*E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align*}
which is nothing but the 1D model in Section \ref{sec:projection_to_1d} after further dropping $u_x, B_y, E_x$. We compare the results produced by the 1D scheme (see Section \ref{sec:1d_fully_discrete_model}) and those produced by the 3D scheme (see Section \ref{sec:3d_ap_scheme}) restricted to the $z$-axis. The following initial conditions are used for both models
\begin{equation*}
    n_e(z,0) = n_i(z,0) = 1, u_z(z,0) = \chi_{[-0.1,0]}(z) - \chi_{[0,0.1]}(z),\ \ \forall z \in [-0.1,0.1].
\end{equation*}
where $\chi$ is the characteristic function. The other variables are initially zero. The case for $\lambda = 1$ is tested. Fig. \ref{fig:z_axis_reduction} demonstrates good matching.

@@

Next, we perform a grid study. Due to the high computational cost in 3D simulations, reference solutions produced by a highly-refined mesh are not available. Therefore, we demonstrate results generated by relatively coarse meshes. Tab. \ref{tab:grid_study_norm} lists $L^2$-norms of the solutions on different meshes, which indicates robustness with respect to mesh refinement. To reveal more features of the solutions, in Fig. \ref{fig:grid_study_3d_clip_lambda-1e-1} (for $\lambda = 0.1$) and \ref{fig:grid_study_3d_clip_lambda-0} (for $\lambda = 0$) we plot the solutions at the cross-section generated by meshes of different sizes on which qualitatively the same solutions are observed.

@@

The stabilization proposed in Section \ref{sec:reform-discrete} is essential to achieve a stable result when $\lambda$ tends to zero. As is shown in Fig. \ref{fig:stabilization_comparison}, the scheme without stabilization tends to blow up when $\lambda$ is close to zero while the one with stabilization remains stable. 
\begin{figure}
    \centering
    \includegraphics{stabilizationComparision_stepVoltage.eps}
    \caption{Case II: Stabilization in the non-conducting domain $\Omega_N$. The $\mathbf{E}$-field z-component in a boundary cell in $\Omega_N$ is displayed over time. }
    \label{fig:stabilization_comparison}
\end{figure}

@@

\section{Conclusion}
We have developed an AP scheme for the Euler-Maxwell plasma model in three spatial dimensions that is versatile in both non-neutral $\lambda = \mathcal{O}(1)$ and quasi-neutral $\lambda \rightarrow 0$ regimes. The main features of our work lie in: i) Maxwell's equations are discretized on primal and dual meshes by FIT (in the spirit of DEC). By discretizing the Euler equations by FVM on dual mesh, the coupling of two systems is naturally realized via the connection of the mass flux and electric current at each dual face. ii) A non-conducting region is taken into account where additional stabilization is essential when $\lambda \rightarrow 0$. We enforce the vanishing divergence of the $\mathbf{D}$-field through a Lagrange multiplier for any value of $\lambda$. iii) The alignment of primal-dual meshes at the boundary entails cut-off cells and auxiliary unknowns have to be introduced. iv) A lumping trick is applied to the conductivity matrix (relating the electric current and the electric field) to enhance stability.

Our approach has been tested on a cylindrical domain with ECE boundary conditions and the AP property has been verified numerically. To the best of the authors' knowledge, this work is among the first to try to solve the 3D fluid plasma model on unstructured meshes, which potentially gives more flexibility than the finite-difference-based approaches and reduces the computational cost compared to particle-based approaches. In particular, the AP property allows us to address regimes of the arbitrary value of the Debye length.

\todo{Polish the reference}
\bibliography{ref}
\end{document}
